---
title: "flat_ppackage.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Internal Datasets

## Schools List

```{r function-schools}
#' schools
#'
#' Table of School Codes and School Name/Type.
#'
#' @format A data frame with 140 rows and 3 variables:
#' \describe{
#'   \item{ SchoolCode }{ character }
#'   \item{ SchoolName }{ character }
#'   \item{ SchoolLevel }{ character }
#' }
#' @source Aspen 
#' 

# Make the dataset file available to the current Rmd during development
# pkgload::load_all(path = here::here(), export_all = FALSE)

#The school data file was created in aspen with a "quick report"
#called "School_List." It exports a row for every student, so 
#drop the header, run sort -u, and then add the header back and
#save as schools.csv.
#datafile <- system.file("schools.csv", package = "PPackage")
schools <- read.csv("inst/schools.csv", encoding = "UTF-8")[,c(1,2,4)]
"schools"
schools
```


# Pretty-print a percentage

```{r function-paste_perc}
#' Convert decimal value to a percent to be printed
#'
#' @param x double or vector of doubles
#' @inheritParams base::paste0
#' @inheritParams base::round 
#'
#' @return
#' Character vector of a percent value
#' @export
#'
#' @examples
paste_perc <- function(x, digits = 0) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  base::paste0(base::round(x*100, digits = digits), "%")
}
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r examples-paste_perc}
x = 0.988
paste_perc(x)

x = c(0.444444, 0.2222, 0.5555)
paste_perc(x, 1)
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->

```{r tests-paste_perc}
test_that("paste_perc works properly and show error if needed", {
  expect_true(paste_perc(0.5) == "50%")
  expect_true(all(paste_perc(c(0.444444, 0.2222), 1) == c("44.4%", "22.2%")))
  expect_error(paste_perc("text"))
})

```

# Calculate the mean of a vector

<!--
There can be other functions, examples and tests in your flat template.
Each of them will be inflated in a different file, provided that there is a level-1 or level-2 section title to separate from previous functions.
-->

## Use sub-functions in the same chunk

```{r function-my_other_median}
#' My Other median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_other_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  sub_median(x, na.rm =na.rm)
}

#' Core of the median not exported
#' @param x Vector of Numeric values
#' @inheritParams stats::median
sub_median <- function(x, na.rm = TRUE) {
  stats::median(x, na.rm)
}
```

```{r examples-my_other_median}
my_other_median(1:12)
```

```{r tests-my_other_median}
test_that("my_median works properly and show error if needed", {
  expect_true(my_other_median(1:12) == 6.5)
  expect_error(my_other_median("text"))
})
```

<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_ppackage.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
